The importance of measurement uncertainty in ecological management

### 2018-01-12 appendix/appendixB.Rmd
results discussion WIP tweaking plots

@@

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "appendixB_alphas"
```

@@

```{r}
meta <- expand.grid(commonname = pars$commonname, 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
  left_join(pars) %>%
  mutate(scenario  = as.character(1:length(sigma_m)))

@@

```{r}
sims <- pomdp_sims %>% 
  mutate(optimal = states[optimal] * N) %>% # original scale
  select(year, optimal, commonname, sigma_m) %>%
  rename(stock = optimal) %>% 
  ## treat each sigma_m value as separate 'model'
  mutate(sigma_m = as.factor(sigma_m)) %>%
  mutate(model = recode(sigma_m, 
                        "0" = "Reed",
                        "0.1" = "POMDP", 
                        "0.2" = "POMDP_0.2")) %>%
  select(-sigma_m) %>%
  bind_rows(historical)

write_csv(sims,"appendixB_files/sims.csv")
```

>>>>

```{r plotting}
library(gridExtra)
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors

colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
```

@@

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "../data/ram_ex"
```

@@

```{r}
meta <- expand.grid(commonname = pars$commonname, 
                    sigma_m = c(0, 0.1, 0.15),
                    stringsAsFactors = FALSE) %>%
  left_join(pars) %>%
  mutate(scenario  = as.character(1:length(sigma_m)))

@@

```{r}
sims <- pomdp_sims %>% 
  mutate(optimal = states[optimal] * N) %>% # original scale
  select(year, optimal, commonname, sigma_m) %>%
  rename(stock = optimal) %>% 
  ## treat each sigma_m value as separate 'model'
  mutate(sigma_m = as.factor(sigma_m)) %>%
  mutate(model = recode(sigma_m, 
                        "0" = "Reed",
                        "0.1" = "POMDP", 
                        "0.15" = "POMDP_0.15")) %>%
  select(-sigma_m) %>%
  bind_rows(historical)

write_csv(sims,file.path(log_dir, "ram_ex.csv"))
```

### 2018-01-12 appendix/appendix_harvestfirst.Rmd
results discussion WIP tweaking plots

x0 <- K/6
Tmax = 20
do_det_sim <- function(policy, f, x0, Tmax){
    action <- state <- obs <- as.numeric(rep(NA,Tmax))
    state[1] <- x0

@@

@@

```{r}
det_sims %>%
  ggplot(aes(time, state, col=method)) + 
  geom_line() + 
  geom_hline(aes(yintercept=B_MSY), lwd=1)

>>>>

x0 <- K/6
Tmax = 100
do_det_sim <- function(policy, f, x0, Tmax){
    action <- state <- obs <- as.numeric(rep(NA,Tmax))
    state[1] <- x0

@@

write_csv(det_sims, "../data/observe_harvest_recruit/det_sims.csv")
```

@@

```{r fig.width=3.5, fig.height=3.5}
det_sims %>%
  mutate(method = fct_recode(method, 
                             "CE" = "det",
                             "TAC" = "pgy",
                             "MSY" = "msy")) %>%
  ggplot(aes(time, state, col=method)) + 
  geom_line(lwd=1) + 
  scale_color_manual(values = colors) +
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

### 2018-01-12 manuscripts/manuscript.Rmd
results discussion WIP tweaking plots

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(4)
berkeley_colors <- c("#D9661F", "#3B7EA1", "#FDB515", "#6C3302",  "#00B0DA",  "#CFDD45")
```

@@

Figure 1 shows average fish biomass

```{r fig.width=7, fig.height=3.5, fig.cap="Average fish biomass under different management strategies under increasing levels of measurement uncertainty. Each plot the mean stock size over time across 100 replicate simulations under each policy: constant escapement, maximum sustainable yield (MSY), and the porposed partially observed Markov decision process (POMDP) method. Measurement error increases as a normal distribution with standard deviation 0, 0.1, or 0.15, as indicated at the top of the panel.  Environmental stochasticity is fixed a standard deviation of 0.15 in each panel.  Carrying capacity K normalized to 1, r = 0.75. Additional environmental noise levels and comparison to MSY rather than TAC can be found in the supplementary material."}
sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/sims.csv"), col_types = "inicnn")
sims %>%
  filter(method != "msy", sigma_g == "0.15") %>%
  mutate(method = fct_recode(method, 
                             "Constant escapement" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  group_by(time, method, sigma_m) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line() + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  facet_wrap(~ sigma_m, labeller = label_bquote(sigma[m] == .(sigma_m))) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

@@

```{r fig.width=3.5,fig.height=3.5, fig.cap=""}
all_policies <- read_csv(file.path(log_dir, "observe_harvest_recruit/all_policies.csv"))
all_policies %>% 
  filter(policy %in% c("low", "medium", "det", "pgy")) %>%
  mutate(policy = fct_recode(policy,
                             "Constant escapement" = "det",
                             "TAC" = "pgy",
                             "POMDP: low prior" = "low",
                             "POMDP: medium prior" = "medium"
                             )) %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = c("black", berkeley_colors) ) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```

```{r message=FALSE, warning=FALSE, fig.width=3.5, fig.height = 7, fig.cap="Comparisons of harvest level that would be recommended by policies considered here relative to historical harvest levels in two commercial fish stocks.  POMDP solution assumes a measurement error of 10%."}
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))
ram_ex %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy")) %>%
   mutate(model = fct_recode(model,
                             "Constant escapement" = "Reed",
                             "TAC" = "pgy"
                             )) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", berkeley_colors)) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors
```

@@

```{r load_data, message=FALSE, warning=FALSE}
sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/sims.csv"), col_types = "inicnn")
det_sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/det_sims.csv"))
all_policies <- read_csv(file.path(log_dir, "observe_harvest_recruit/all_policies.csv"))
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))

colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))

```

Figure 1 shows average fish biomass across 100 replicate simulations under three different management strategies: constant escapement (CE), total allowable catch (TAC; equal to 80% MSY), and partially observed Markov decision process (POMDP) management.  Each successive panel shows a subsequently higher level of measurement error, from $\sigma_m = 0$, $\sigma_m = 0.1$, and $\sigma_m = 0.15$, as indicated.  Standard deviation from the mean across replicate simulations is shown as faint colored bands, indicating significant variation due to stochasticity between individual replicates.  In each panel shown in Figure 1 stochastic recruitment (environmental noise) is set to a moderate $\sigma_g = 0.15$.  In the absence of either environmental noise or measurement error (Supplemental material, Figure S1) POMDP, CE, and MSY would converge to stock at the $B_{MSY}$, while TAC would maintain the stock at a slightly higher level.  The first panel of Figure 1 shows that the the introduction of stochastic growth has a significant negative impact on the TAC strategy (This impact is even more severe for MSY, which always harvests strictly more than TAC by definition, as, shown in Supplemental material Figure S2), which results in an average biomass significantly lower than $B_{MSY}$.  Without mesasurement error, the CE and POMDP strategies are nearly identical with both approximately maintaining the stock at $B_{MSY}$ despite the significant environmental stochasticity.  As measurement error increases in the subsequent panels, CE and TAC strategies perform increasingly poorly, while the POMDP continues to maintain the average stock close to $B_{MSY}$.  Notably, CE is significantly more impacted by measurement uncertainty than TAC, with CE averaging even lower biomass than TAC under moderate measurement uncertainty.

Figure 1 confirms that the precautionary approach represented by the TAC does indeed prove more robust to the problem of measurement error than the optimization solution represented by CE.  In general, we expect that the rigid assumptions required of optimization will lead to worse outcomes when those assumptions are not met than we see under the corresponding heuristic approach.  Yet it is important to bear in mind that the opposite pattern was observed in the case of environmental stochasticity, in which it was the heuristic TAC stategy rather than the CE strategy that lead to the highest overfishing rate.  In contrast, the POMDP approach successfully handles both stochasticity and observation error, maintaining the stock near $B_{MSY}$ levels that produce the highest yield.

<!-- Show results of POMDP when over-estimating! -->

```{r fig.width=7, fig.height=3.5, fig.cap="Average fish biomass under different management strategies under increasing levels of measurement uncertainty. Each plot the mean stock size over time across 100 replicate simulations under each policy: constant escapement (CE), Total allowable catch (TAC = 80% MSY), and the proposed partially observed Markov decision process (POMDP) method. Measurement error increases as a normal distribution with standard deviation 0, 0.1, or 0.15, as indicated at the top of the panel.  Environmental stochasticity is fixed a standard deviation of 0.15 in each panel.  Carrying capacity K normalized to 1, r = 0.75. Additional environmental noise levels and comparison to MSY rather than TAC can be found in the supplementary material."}
sims %>%
  filter(method != "msy", sigma_g == "0.15") %>%
  mutate(method = fct_recode(method, 
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  group_by(time, method, sigma_m) %>%
  summarise(mean = mean(state), sd = sd(state)) %>% 
  mutate(sigma_m = as.character(sigma_m)) ->
fig1_df

fig1_df %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd=1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  facet_wrap(~ sigma_m, labeller = label_bquote(sigma[m] == .(sigma_m))) + 
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

@@

```{r fig.width=7,fig.height=3.5, fig.cap=""}
all_policies %>% 
  filter(policy %in% c("low", "medium", "det", "pgy")) %>%
  mutate(policy = fct_recode(policy,
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP: low prior" = "low",
                             "POMDP: medium prior" = "medium"
                             )) -> policy_df
policy_df %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```
```{r fig.width=7,fig.height=3.5, fig.cap=""}
policy_df %>%
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```

```{r message=FALSE, warning=FALSE, fig.width=7, fig.height = 3.5, fig.cap="Comparisons of harvest level that would be recommended by policies considered here relative to historical harvest levels in two commercial fish stocks.  POMDP solution assumes a measurement error of 10%."}
ram_ex %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy")) %>%
   mutate(model = fct_recode(model,
                             "CE" = "Reed",
                             "TAC" = "pgy"
                             )) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = colors) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```
